Recursive Neural Network Part-of-Speech Tagger

### 2013-12-20 paper/paper.tex
Add your correct email addresses.

\author{Hao Liu \\
  NYU \\
  {\tt email@domain} \\\And
  Jiali Huang \\
  NYU \\
  {\tt email@domain} \\\And
  Robert Dionne \\
  NYU \\
  {\tt robertsdionne@nyu.edu} \\}

>>>>

\author{Hao Liu \\
  NYU \\
  {\tt haoliu@nyu.edu} \\\And
  Jiali Huang \\
  NYU \\
  {\tt jiali.huang@nyu.edu} \\\And
  Robert Dionne \\
  NYU \\
  {\tt robertsdionne@nyu.edu} \\}
